Diffantom: a software layer to build digital phantoms of whole-brain diffusion MRI

### 2015-08-12 paper/main.tex
follow suggestion of EC. fix #21

\noindent\textbf{\textit{Implementation and reproducibility\textcolon}\label{sec:data_workflow}} %
We also provide a full software layer to produce \emph{diffantoms} from real \gls*{dmri} datasets
  drawn from the \gls*{hcp}.
This workflow, presented in \autoref{fig:figure1}, is implemented using
  \emph{nipype} \citep{gorgolewski_nipype_2011} to ensure reproducibility and usability.

>>>>

\noindent\textbf{\textit{Implementation and reproducibility\textcolon}\label{sec:data_workflow}} %
We also provide the full software stack used to generate \emph{diffantoms}, so that users can
  regenerate similar datasets with different parameters.
This workflow, presented in \autoref{fig:figure1}, is implemented using
  \emph{nipype} \citep{gorgolewski_nipype_2011} to ensure reproducibility and usability.
